raw-to-full

### 2017-04-16 raw-to-full.Rmd
stuff

```{r}
DSM_temps <- read.csv("raw-data/DSM_temps.csv")
FAR_temps <- read.csv("raw-data/FAR_temps.csv")
MSN_temps <- read.csv("raw-data/MSN_temps.csv")
MSP_temps <- read.csv("raw-data/MSP_temps.csv")
ORD_temps <- read.csv("raw-data/ORD_temps.csv")

temps <- rbind(DSM_temps, FAR_temps, MSN_temps, MSP_temps, ORD_temps)

>>>>

```{r}
DSM_temps <- read.csv("raw-data/DSM_temps.csv")
FAR_temps <- read.csv("raw-data/FAR_temps.csv")
MSN_temps <- read.csv("raw-data/MSN_temps.csv")
MSP_temps <- read.csv("raw-data/MSP_temps.csv")
ORD_temps <- read.csv("raw-data/ORD_temps.csv")
FSD_temps <- read.csv("raw-data/FSD_temps.csv")
STL_temps <- read.csv("raw-data/STL_temps.csv")

temps <- rbind(DSM_temps, FAR_temps, MSN_temps, MSP_temps, ORD_temps, FSD_temps, STL_temps)
